### 2024-03-25 mycv/subs/fundings.tex
snapshot

  \cvhonor
  {Multi-scale crystal plasticity framework for multiphase metals under non-linear forming scenario} %Award
  {NRF-2017R1D1A1B03031052}%EVENT
  {National Science Foundation of Korea} %Location
  {2017-2020} %dates

>>>>

  \cvhonor
  {자동차용 경량소재 가상공학 플랫폼 구축}
  {}
  {\href{http://www.motie.go.kr/www/main.do}{South Korean Ministry of Trade, Industry and Energy}}
  {2018-2021}

  \cvhonor
  {Technology development for flame retardant eco hybrid composites}
  {}
  {NSF of Korea}
  {2018-2027}

  \cvhonor
  {Multi-scale crystal plasticity framework for multiphase metals under non-linear forming scenario} %Award
  {책임; NRF-2017R1D1A1B03031052}%EVENT
  {NSF of Korea} %Location
  {2017-2020} %dates
